Destruction of metrizability in generalized inverse limits

### 2015-09-17 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
add reference generalizing kappa from omega, add note of open question about Gamma for non-continuum valued maps

Ingram and Mahavier showed in \cite{i m paper} that $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is non-empty and compact. They also found that
if $f_{\alpha \beta}$ is always continuum-valued, then $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is also connected, and therefore a Hausdorff continuum. Greenwood and Kennedy showed in \cite{greenwood kennedy} that there is a non-continuum-valued u.s.c. surjective idempotent bonding map $f$ for which $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is disconnected.

@@

Let us say a subset $S$ of $[0,1]^2$ satisfies condition $\Gamma$ if, for some $x, y \in [0,1]$ with $x \ne y$, $\<x,x\> \in S$, $\<y,y\> \in S$, and either $\<x,y\>$ or $\<y,x\> \in S$; see Figure \ref{conditionGamma}. Let $\Delta = \{\<a,a\> \ | \ a \in [0,1]\}$, and notice that $[0,1]^2 \setminus \Delta$ is the union of two disjoint open sets.

@@

>>>>

Ingram and Mahavier showed in \cite{i m paper} that $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is non-empty and compact. They also found that
if $f_{\alpha \beta}$ is always continuum-valued, then $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is also connected, and therefore a Hausdorff continuum. Varagona generalized these results for other index sets (including ordinals $\kappa$) in Theorems 2.1 and 2.2 of \cite{varagona}. Greenwood and Kennedy showed in \cite{greenwood kennedy} that there is a non-continuum-valued u.s.c. surjective idempotent bonding map $f$ for which $\varprojlim \{X_{\alpha}, f, \omega\}$ is disconnected.

@@

Let us say a subset $S$ of $[0,1]^2$ satisfies \textit{condition $\Gamma$} if, for some $x, y \in [0,1]$ with $x \ne y$, $\<x,x\> \in S$, $\<y,y\> \in S$, and either $\<x,y\>$ or $\<y,x\> \in S$; see Figure \ref{conditionGamma}. Let $\Delta = \{\<a,a\> \ | \ a \in [0,1]\}$, and notice that $[0,1]^2 \setminus \Delta$ is the union of two disjoint open sets.

@@

Note that while we have assumed that $f:[0,1]\to C([0,1])$ (which also guarantees that the inverse limit is a continuum), it is an open question whether $\Gamma$ must also hold for any surjective idempotent u.s.c. $f:[0,1]\to 2^{[0,1]}$ (regardless if the inverse limit remains connected).
